---
name: Jake Rozran
position: "Data Science Practice Lead & Adjunct Professor of Data Science"
address: "1400 Maryland Ave. Havertown, PA 19083"
phone: (410) 231-9371
www: jakelearnsdatascience.com
email: "jacob.rozran@gmail.com"
twitter: StatsManPHL
github: jrozra200
linkedin: jacob-rozran
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(VennDiagram)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Summary

- Data & technology professional with 8+ years of real-world experience in data 
science (using SQL, R, and Python), working in cross functional teams (including 
Product, Engineering, and Operations), and owning workflows from ideation to 
production (putting ML into production).
- Curious about the changing landscape of technology's impact on our lives 
and especially passionate about fair and ethical algorithms.
- Able to explain complex subjects to all levels of understanding as an 
Adjunct Professor of Data Science & Statistics & Data Science Practice Lead. 

# Top Skills & Technologies

\begin{center}

```{r, results = "asis"}
df <- data.frame(a = c("SQL", "Python", "R", "Bash", "HTML"),
                 b = c("PostgreSQL", "Hive/Impala (Hadoop)", "Athena (AWS)", 
                       "SQL/mySQL/SQLite", "Oracle"),
                 c = c("Jupyter Notebooks", "RStudio", "GitHub", 
                       "Tableau/Metabase/Redash", "MS Office Suite"),
                 d = c("Data Ethics", "Data Visualization", 
                       "Data Analysis", "Project Management", 
                       "People Leadership"))

names(df) <- c("LANGUAGES", "DATABASES", "APPLICATIONS", "METHODS")

kable(df, row.names = FALSE, "latex", booktabs = T)
```
\end{center}

# Experience

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates,
        "Data Science Practice Lead", 
        "CivicActions", 
        "Lafayette, CA", 
        "Feb 2021 - Present"
        ) %>% detailed_entries(role, dates, company, loc)
```

- **Summary:** Building a Data Science Practice Area with > $1MM revenue after 
12 months; personally focused on data science, people management and coaching, 
sales, marketing, and project management.

- **Impactful Analysis:** For the Centers of Medicare and Medicaid (CMS), 
leveraging Natural Language Processing (NLP) in the creation and evaluation of 
System Security Plans (SSPs) to optimize the Authority to Operate (ATO) process; 
analyzing AWS usage to forecast annual usage and identify inefficiencies; 
using graph analysis and NLP to identify related documents to provide enhanced 
search capabilities.

- **Databases (SQL):** Accessing data from AWS Athena (at CMS) and ClickHouse 
(internal data).

- **Scripting (Python/R):** At CMS, I utilize Python for NLP projects and R to 
build Shiny Dashboards and complete bespoke analysis (mainly in RMarkdown 
documents).

- **Ownership, Dealing with Ambiguity, & Communication:** As the first data 
science teammate on each project I have supported (and at the company), I have 
had to focus on explaining the capabilities of our team and iteratively working 
with clients to understand their needs and providing relevant analysis.

- **Partnership:** Internally, I work hand in hand with our marketing, program 
management, and sales teams to identify new opportunities for our data science 
practice area; externally, on each project, I work closely with our clients, 
product owners, engineering teams, and design teams.

- **Personal Impact:** One of five members of the company's Diversity, Equity, 
Inclusion, and Accessibility (DEIA) team; responsible for helping improve the 
company's DEIA practices, including analyzing demographic data, designing 
surveys to understand company feeling about DEIA, and identifying and improving 
company policy to be more inclusive.

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates,
        "Adjunct Professor of Data Science & Statistics", 
        "Villanova University", 
        "Villanova, PA", 
        "Aug 2020 - Present"
        ) %>% detailed_entries(role, dates, company, loc)
```

- **Ownership & Communication:** Build the syllabus, lectures, assignments, 
projects, and tests for undergraduate Data Science, Intro to Statistics, and 
Intro to Statistics for Biology courses.

- **Personal Impact:** Advise and mentor students by writing recommendations for 
various programs, helping guide studies for real-world success after graduation, 
and providing assistance through the stresses of university life.

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates,
        "Public Interest Technology - University Network (PIT-UN) Evaluation Committee", 
        "New America", 
        "Washington, DC", 
        "June 2022 - July 2022"
        ) %>% detailed_entries(role, dates, company, loc)
```

- **Summary:** Evaluated proposals seeking funding to educate students who can 
better apply technical understanding and practice to questions of individual 
rights, justice, social welfare, and the public good, particularly for those 
members of our society least well served historically and today by existing 
systems and policies. 

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates,
        "Solutions Consultant", 
        "Socure", 
        "New York, NY", 
        "Jan 2020 - Feb 2021"
        ) %>% detailed_entries(role, dates, company, loc)
```

- **Summary:** Technical expert on fraud prevention, Know Your Customer 
(KYC)/Customer Identification Program (CIP), Socure product modules, data 
science, statistics, and data visualization in support of the sales and 
onboarding processes.

- **Analysis, Communication, & Dealing with Ambiguity:** Created custom 
proof-of-concept (POC) analyses for prospective customers - showing the value of 
Socure versus their current solution(s).

- **Ownership:** Served as the Growth Team's subject matter expert (SME) on data 
science, creating educational documents and presentations on challenging topics 
like Area Under the Curve (AUC), false positives, and other model evaluation 
criteria.

- **Partnership:** Worked with the Marketing Team to create content for the 
Socure Blog on machine learning techniques.

- **Personal Impact:** Member of the DEI team.

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates,
        "Manager of Data Analytics", 
        "Xfinity Mobile Risk Management (Comcast)", 
        "Philadelphia, PA", 
        "Mar 2017 - Jan 2020"
        ) %>% detailed_entries(role, dates, company, loc)
```

- **Summary:** Led and managed the data analytics and engineering team for 
Xfinity Mobile Credit Risk Management, including hiring and training of staff 
analysts and engineers, collaborating with and providing analysis for 
stakeholders, and tracking and prioritizing all team tasking.

- **Ownership & Dealing with Ambiguity:** Invented, designed, and put into 
production a fraud decision making tool that was responsible for a decrease in 
month-over-month fraud losses by 92% in 2018 - this tool was implemented while 
our team dealt with procurement and staffing issues.

- **Impactful Analysis & Communication:** Built and maintained the executive 
reporting packages for both fraud and credit risk management.

- **Partnership:** Worked closely with product, engineering, and operations 
teams to handle all aspects of risk management decision making (fraud and 
credit).

- **Databases (SQL):** Leveraged, maintained, and created tables in both Impala 
(Hadoop) and Oracle.

- **Scripting (Python/R):** Built a fraud decision making tool that combines 
custom feature creation, statistical and business rules, and predictive models 
built in Python, R, and Bash. 

- **Personal Impact:** Provided coaching, leadership, and mentorship to all 
analysts on the Xfinity Mobile Risk Management team.

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates,
        "Senior Data Analyst", 
        "Internet Services Engineering (Comcast)", 
        "Philadelphia, PA", 
        "Sep 2014 - Mar 2017"
        ) %>% detailed_entries(role, dates, company, loc)
```

- **Impactful Analysis:** Designed and built predictive models, which improved 
compromised user account detection times and discovery accuracy – this work was 
presented internally along with several internal blog posts about the effort.

- **Impactful Analysis:** Created forecasts of user base growth and project 
completion.

- **Databases (SQL):** Obtained data from Splunk using the Splunk Query Language.

- **Scripts (Python/R):** Utilized R and Python to build and interpret Logisitic 
Regression Models.

- **Partnership:** Worked closely with the product, project, and engineering 
teams to identify and correctly prioritize analyses. 

---

\begin{center}

Additional work experience is outlined on my LinkedIn Profile.

\end{center}

# Volunteer
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Resident Data Science Expert", "Govern for America", "Katonah, NY", "April 2022 - Present", "Provide training and mentorship in data science, data visualization, and data ethics for GFA fellows."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Organizer", "Data Jawn Conference", "Philadelphia, PA", "April 2019 - Present", "Assisted in promotion, speaker selection, and day-of-event logistics for the Data Jawn, a Philadelphia data conference highlighting the great work of our local data commnuity."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Data Analyst", "Montgomery County Public Defender", "Norristown, PA", "May 2016 - Jun 2017", "Assisted Montgomery County Public Defender to define an analytics strategy to support competitive salaries and fair defence for all Montgomery County residents; created, built, and maintained advanced analysis."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

# Education
```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, 
        "Masters of Science - Applied Statistics", "Villanova University", "Villanova, PA", "2015 - 2017"
        ) %>% detailed_entries(degree, dates, uni, loc)
```

```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative for Student Lobbying Day in Harrisburg, PA, 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Traditions Council Treasurer, 2007 - 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Dean’s List, 2006, 2008",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative to Colonial Athletic Association's Student Athlete Advisory Committee, 2006",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Varsity Soccer Player, 2004 - 2006"
        ) %>% detailed_entries(degree, dates, uni, loc, details)
```

