---
name: Jake Rozran
position: "Senior Manager of Data Science & Adjunct Professor of Data Science"
address: "1400 Maryland Ave. Havertown, PA 19083"
phone: (410) 231-9371
www: jakelearnsdatascience.com
email: "jacob.rozran@gmail.com"
twitter: StatsManPHL
github: jrozra200
linkedin: jacob-rozran
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include = FALSE}
library(tidyverse)
library(vitae)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Summary

- Data & technology professional with 9+ years of real-world experience 
(at Fortune 10, start-up, and consulting companies) in data science and 
analytics (using R and Python).
- Passionate about coaching and teaching, leading teams, and diving into data to 
understand the meaning and nuance, all while being able to simply explain to 
all levels of the organization. 
- Curious about the changing landscape of technology's impact on our lives 
and minds and especially curious about fair and ethical algorithms.

# Top Skills & Technologies

\begin{center}

```{r, results = "asis"}
df <- data.frame(a = c("R", "Python", "SQL", "Bash", "HTML/MD"),
                 b = c("Athena (AWS)", "BigQuery (Google)", 
                       "Hive/Impala (Hadoop)", "SQL/mySQL/SQLite", "PostgreSQL"),
                 c = c("RStudio", "Jupyter Notebooks", "GitHub", 
                       "Tableau", "MS Office Suite"),
                 d = c("Data Analysis", 
                       "Data Visualization", "People Leadership", 
                       "Project Management", "Data Ethics"))

names(df) <- c("LANGUAGES", "DATABASES", "APPLICATIONS", "METHODS")

kable(df, row.names = FALSE, "latex", booktabs = T)
```
\end{center}

# Experience

```{r}
tribble(
    ~ role, ~ company, ~ loc, ~ dates, ~details,
    "Senior Manager of Data Science", 
    "Comcast", 
    "Philadelphia, PA", 
    "Jan 2023 - Present",
    "Manage a data science team of four that is responsible for the creation, analysis, and maintenance of multiple customer facing machine learning
models that improve and monitor the reliability of Comcast’s Network.",
    "Senior Manager of Data Science", 
    "Comcast", 
    "Philadelphia, PA", 
    "Jan 2023 - Present",
    "As a player/coach, I spend part of my day coding and doing analysis and part of my day providing team leadership.",
    "Senior Manager of Data Science", 
    "Comcast", 
    "Philadelphia, PA", 
    "Jan 2023 - Present",
    "Work closely with organization leadership, product managers, and outside organizations to identify and communicate priorities, statuses, and issues.",
    "Senior Manager of Data Science", 
    "Comcast", 
    "Philadelphia, PA", 
    "Jan 2023 - Present",
    "Implement and continually revise best practices for data science and analytics workflows - improving peer and code review practices, time spent in meetings, and work prioritization.",
    "Senior Manager of Data Science", 
    "Comcast", 
    "Philadelphia, PA", 
    "Jan 2023 - Present",
    "Meet regularly with the individual team members to recieve feedback, provide coaching, and understand member's goals.",
    "Senior Manager of Data Science", 
    "Comcast", 
    "Philadelphia, PA", 
    "Jan 2023 - Present",
    "Tools used: R/RStudio, Python/PySpark/Jupyter Notebooks, AWS: Athena/Glue/Redshift, Tableau"
) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
    ~ role, ~ company, ~ loc, ~ dates, ~details,
    "Adjunct Professor of Data Science & Statistics", 
    "Villanova University", 
    "Villanova, PA", 
    "Aug 2020 - Present",
    "Build the syllabus, lectures, assignments, projects, and tests for undergraduate Data Science, Intro to Statistics, and Intro to Statistics for Biology courses.",
    "Adjunct Professor of Data Science & Statistics", 
    "Villanova University", 
    "Villanova, PA", 
    "Aug 2020 - Present",
    "Advise and mentor students by writing recommendations for various programs, helping guide studies for real-world success after graduation, and providing assistance through the stresses of university life.",
    "Adjunct Professor of Data Science & Statistics", 
    "Villanova University", 
    "Villanova, PA", 
    "Aug 2020 - Present",
    "Frequently serve as a guest lecturer for the Mathematics and Stastics department on what it is like to be a data professional in industry."
) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~details,
        "Public Interest Technology - University Network (PIT-UN) Evaluation Committee", 
        "New America", 
        "Washington, DC", 
        "June 2022; June 2023", 
        "Evaluated proposals seeking funding to educate students who can better apply technical understanding and practice to questions of individual rights, justice, social welfare, and the public good, particularly for those members of our society least well served historically and today by existing systems and policies. "
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~details,
        "Data Science Practice Lead", 
        "CivicActions", 
        "Lafayette, CA", 
        "Feb 2021 - Jan 2023", 
        "Building a Data Science Practice Area with > $1MM revenue after 12 months; personally focused on data science, people management and coaching, sales, marketing, and project management.",
        "Data Science Practice Lead", 
        "CivicActions", 
        "Lafayette, CA", 
        "Feb 2021 - Jan 2023",
        "For the Centers of Medicare and Medicaid (CMS), leveraging Natural Language Processing (NLP) in the creation and evaluation of System Security Plans (SSPs) to optimize the Authority to Operate (ATO) process; analyzing AWS usage to forecast annual usage and identify inefficiencies; using graph analysis and NLP to identify related documents to provide enhanced search capabilities.",
        "Data Science Practice Lead", 
        "CivicActions", 
        "Lafayette, CA", 
        "Feb 2021 - Jan 2023",
        "As the first data science teammate on each project I have supported (and at the company), I have  had to focus on explaining the capabilities of our team and iteratively working with clients to understand their needs and providing relevant analysis.",
        "Data Science Practice Lead", 
        "CivicActions", 
        "Lafayette, CA", 
        "Feb 2021 - Jan 2023",
        "Internally, I work hand in hand with our marketing, program management, and sales teams to identify new opportunities for our data science practice area; externally, on each project, I work closely with our clients, product owners, engineering teams, and design teams.",
        "Data Science Practice Lead", 
        "CivicActions", 
        "Lafayette, CA", 
        "Feb 2021 - Jan 2023",
        "Internally, I work hand in hand with our marketing, program management, and sales teams to identify new opportunities for our data science practice area; externally, on each project, I work closely with our clients, product owners, engineering teams, and design teams.",
        "Data Science Practice Lead", 
        "CivicActions", 
        "Lafayette, CA", 
        "Feb 2021 - Jan 2023",
        "One of five members of the company's Diversity, Equity, Inclusion, and Accessibility (DEIA) team; responsible for helping improve the company's DEIA practices, including analyzing demographic data, designing surveys to understand company feeling about DEIA, and identifying and improving company policy to be more inclusive.",
        "Data Science Practice Lead", 
        "CivicActions", 
        "Lafayette, CA", 
        "Feb 2021 - Jan 2023",
        "Accessing data from AWS Athena (at CMS) and ClickHouse (internal data). Utilize Python for NLP projects and R to build Shiny Dashboards and complete bespoke analysis (mainly in RMarkdown documents)."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~details,
        "Solutions Consultant", 
        "Socure", 
        "New York, NY", 
        "Jan 2020 - Feb 2021", 
        "Technical expert on fraud prevention, Know Your Customer (KYC)/Customer Identification Program (CIP), Socure product modules, data science, statistics, and data visualization in support of the sales and onboarding processes.",
        "Solutions Consultant", 
        "Socure", 
        "New York, NY", 
        "Jan 2020 - Feb 2021", 
        "Created custom proof-of-concept (POC) analyses for prospective customers - showing the value of  Socure versus their current solution(s).",
        "Solutions Consultant", 
        "Socure", 
        "New York, NY", 
        "Jan 2020 - Feb 2021", 
        "Served as the Growth Team's subject matter expert (SME) on data science, creating educational documents and presentations on challenging topics like Area Under the Curve (AUC), false positives, and other model evaluation criteria.",
        "Solutions Consultant", 
        "Socure", 
        "New York, NY", 
        "Jan 2020 - Feb 2021", 
        "Worked with the Marketing Team to create content for the Socure Blog on machine learning techniques.",
        "Solutions Consultant", 
        "Socure", 
        "New York, NY", 
        "Jan 2020 - Feb 2021", 
        "Member of the DEI team."
        ) %>% detailed_entries(role, dates, company, loc, details)
```


```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~details,
        "Manager of Data Analytics", 
        "Xfinity Mobile Risk Management (Comcast)", 
        "Philadelphia, PA", 
        "Mar 2017 - Jan 2020",
        "Led and managed the data analytics and engineering team for Xfinity Mobile Credit Risk Management, including hiring and training of staff analysts and engineers, collaborating with and providing analysis for stakeholders, and tracking and prioritizing all team tasking.",
        "Manager of Data Analytics", 
        "Xfinity Mobile Risk Management (Comcast)", 
        "Philadelphia, PA", 
        "Mar 2017 - Jan 2020",
        "Invented, designed, and put into production a fraud decision making tool that was responsible for a decrease in month-over-month fraud losses by 92% in 2018 - this tool was implemented while our team dealt with procurement and staffing issues.",
        "Manager of Data Analytics", 
        "Xfinity Mobile Risk Management (Comcast)", 
        "Philadelphia, PA", 
        "Mar 2017 - Jan 2020",
        "Built and maintained the executive reporting packages for both fraud and credit risk management.",
        "Manager of Data Analytics", 
        "Xfinity Mobile Risk Management (Comcast)", 
        "Philadelphia, PA", 
        "Mar 2017 - Jan 2020",
        "Provided coaching, leadership, and mentorship to all analysts on the Xfinity Mobile Risk Management team.",
        "Manager of Data Analytics", 
        "Xfinity Mobile Risk Management (Comcast)", 
        "Philadelphia, PA", 
        "Mar 2017 - Jan 2020",
        "Worked closely with product, engineering, and operations teams to handle all aspects of risk management decision making (fraud and credit).",
        "Manager of Data Analytics", 
        "Xfinity Mobile Risk Management (Comcast)", 
        "Philadelphia, PA", 
        "Mar 2017 - Jan 2020",
        "Leveraged, maintained, and created tables in both Impala (Hadoop) and Oracle. Built a fraud decision making tool that combines custom feature creation, statistical and business rules, and predictive models built in Python, R, and Bash."
        ) %>% detailed_entries(role, dates, company, loc, details)
```


```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~details,
        "Senior Data Analyst", 
        "Internet Services Engineering (Comcast)", 
        "Philadelphia, PA", 
        "Sep 2014 - Mar 2017",
        "Designed and built predictive models, which improved compromised user account detection times and discovery accuracy – this work was presented internally along with several internal blog posts about the effort.",
        "Senior Data Analyst", 
        "Internet Services Engineering (Comcast)", 
        "Philadelphia, PA", 
        "Sep 2014 - Mar 2017",
        "Created forecasts of user base growth and project completion.",
        "Senior Data Analyst", 
        "Internet Services Engineering (Comcast)", 
        "Philadelphia, PA", 
        "Sep 2014 - Mar 2017",
        "Worked closely with the product, project, and engineering teams to identify and correctly prioritize analyses.",
        "Senior Data Analyst", 
        "Internet Services Engineering (Comcast)", 
        "Philadelphia, PA", 
        "Sep 2014 - Mar 2017",
        "Obtained data from Splunk using the Splunk Query Language. Utilized R and Python to build and interpret Logisitic Regression Models.",
        ) %>% detailed_entries(role, dates, company, loc, details)
```

---

\begin{center}

Additional work experience is outlined on my LinkedIn Profile.

\end{center}

# Volunteer
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Resident Data Science Expert", "Govern for America", "Katonah, NY", "April 2022 - Jan 2023", "Provide training and mentorship in data science, data visualization, and data ethics for GFA fellows."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Organizer", "Data Jawn Conference", "Philadelphia, PA", "April 2019 - August 2019", "Assisted in promotion, speaker selection, and day-of-event logistics for the Data Jawn, a Philadelphia data conference highlighting the great work of our local data commnuity."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Data Analyst", "Montgomery County Public Defender", "Norristown, PA", "May 2016 - Jun 2017", "Assisted Montgomery County Public Defender to define an analytics strategy to support competitive salaries and fair defence for all Montgomery County residents; created, built, and maintained advanced analysis."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

# Education
```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, 
        "Masters of Science - Applied Statistics", "Villanova University", "Villanova, PA", "2015 - 2017"
        ) %>% detailed_entries(degree, dates, uni, loc)
```

```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative for Student Lobbying Day in Harrisburg, PA, 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Traditions Council Treasurer, 2007 - 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Dean’s List, 2006, 2008",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative to Colonial Athletic Association's Student Athlete Advisory Committee, 2006",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Varsity Soccer Player, 2004 - 2006"
        ) %>% detailed_entries(degree, dates, uni, loc, details)
```

