---
name: Jake Rozran
position: "Data Professional & Adjunct Professor"
address: "1400 Maryland Ave. Havertown, PA 19083"
phone: (410) 231-9371
www: jakelearnsdatascience.com
email: "jacob.rozran@gmail.com"
twitter: StatsManPHL
github: jrozra200
linkedin: jacob-rozran
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(VennDiagram)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Summary

In addition to being a leader, dad, uncle, & data guy, I am a data & technology 
professional with real-world experience in data science, data analytics, data 
engineering, fraud detection, risk modeling, building and maintaining data teams, 
project management, sales, consulting, and teaching. 

My passion for data and statistics has inspired me to become an Adjunct 
Professor of Statistics, which has improved my ability to explain complex 
subjects to all levels of understanding. I love to learn in general and am a 
data fanatic.

On a more personal note, I love being a husband, father, and uncle. I also love 
being active - soccer, running, cycling, hiking, lifting - and taking pictures 
(usually of my kids).


# Data Science Skills

\begin{center}

```{r, results = "asis"}
df <- data.frame(a = c("Fraud Detection", "Credit Risk Modeling", 
                       "Project Management", "Statistical Modeling", 
                       "Data Visualization"),
                 b = c("RStudio", "Jupyter Notebooks", "Tableau", "Git",
                       "Excel"),
                 c = c("R", "Python", "Bash", "SQL", "Java Script"),
                 d = c("Hive/Impala (Hadoop)", "MySQL", "Oracle", "MongoDB", 
                       "Neo4J"))

names(df) <- c("METHODS", "APPLICATIONS", "LANGUAGES", "DATABASES")

kable(df, row.names = FALSE, "latex", booktabs = T)
```
\end{center}

# Experience
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Data Science Practice Lead", "CivicActions", "San Fransico, CA", "Feb 2021 - Present", "Building a Data Science Practice Area with > $1MM revenue after 6 months; focused on data solutions, people management, sales, marketing, and project management.",
        "Data Science Practice Lead", "CivicActions", "San Fransico, CA", "Feb 2021 - Present", "For the Centers of Medicare and Medicaid (CMS), leveraging Natural Language Processing (NLP) in the creation and evaluation of System Security Plans (SSPs) to optimize the Authority to Operate (ATO) process.",
        "Data Science Practice Lead", "CivicActions", "San Fransico, CA", "Feb 2021 - Present", "For the Centers of Medicare and Medicaid (CMS), analyzing AWS usage to forecast annual usage and identify inefficiencies."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Adjunct Professor of Statistics", "Villanova University", "Villanova, PA", "Aug 2020 - Present", "Build the syllabus, lectures, assignments, and tests for undergraduate Intro to Statistics and Intro to Statistics for Biology courses.",
        "Adjunct Professor of Statistics", "Villanova University", "Villanova, PA", "Aug 2020 - Present", "Advise and mentor students by writing recommendations for various programs, helping guide studies for real-world success after graduation, and providing helping hand and ear through the stresses of university life. "
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Solutions Consultant", "Socure", "New York, NY", "Jan 2020 - Feb 2021", "Technical expert on fraud prevention, Know Your Customer (KYC)/Customer Identification Program (CIP), Socure product modules, data science, statistics, and data visualization in support of the sales and onboarding processes.",
        "Solutions Consultant", "Socure", "New York, NY", "Jan 2020 - Feb 2021", "Created custom proof-of-concept (POC) analyses for prospective customers - showing the value of Socure versus their current solution(s).",
        "Solutions Consultant", "Socure", "New York, NY", "Jan 2020 - Feb 2021", "Served as the Growth Team's subject matter expert (SME) on data science, creating educational documents and presentations on challenging topics like Area Under the Curve (AUC), false positives, and other model evaluation criteria.",
        "Solutions Consultant", "Socure", "New York, NY", "Jan 2020 - Feb 2021", "Worked with the Marketing Team to create content for the Socure Blog on machine learning techniques."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Jan 2020", "Lead and manage the data analytics and engineering team for Xfinity Mobile Credit Risk Management, including hiring and training of staff analysts and engineers, collaborating with and providing analysis for stakeholders, and tracking and prioritizing all team tasking.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Jan 2020", "Designed and built a fraud decision making tool that combines custom feature creation, statistical and business rules, and predictive models built in R, Python, and Bash, which, in large part, is responsible for a decrease in month-over-month fraud losses by 92% in 2018.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Jan 2020", "Forecast involuntary churn (both bad debt and unit loss) for the organization on the numerous segments of our customer base.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Jan 2020", "Built and maintain numerous Tableau and Splunk dashboards representing fraud and credit to the organization.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Jan 2020", "Provide coaching, leadership, and mentorship to all analysts on the Xfinity Mobile Risk Management team."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Designed and built predictive models, which improved compromised user account detection times and discovery accuracy – this work was presented internally along with several internal blog posts about the effort.", 
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Used statistical methods to discover and automate the detection of anomalies.", 
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Created forecasts of user base growth and project completion.",
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Maintained and monitored KPIs for multiple application teams within the organization."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Served as a Project Manager and ScrumMaster for the Messaging Application Engineering (MAE) team, responsible for Residential Voicemail and Email Engineering teams.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Obtained my Project Management Professional (PMP) and Certified ScrumMaster (CSM) certifications.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Instituted and evangelized Scrum on both the email and voicemail teams, migrating from a hybrid of waterfall and Kanban, which led to higher team productivity, better communication across teams from development through deployment to production, and improved interaction with our product owners.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Managed the scheduling and owned the priorities for multiple work streams and teams."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Implementation Manager", "NCS Main Study Information Management Systems Project (Booz Allen Hamilton)", "Rockville, MD", "Nov 2010 - Apr 2013", "Served as the Implementation Manager and Site Administrator for the National Children’s Study (NCS) Portal, a Microsoft SharePoint 2010 web application, the NCS Application Homepage, and NCS Password Self Service.",
        "Implementation Manager", "NCS Main Study Information Management Systems Project (Booz Allen Hamilton)", "Rockville, MD", "Nov 2010 - Apr 2013", "Developed a configuration change process for the NCS Portal that streamlined the enhancement process for the site and provided the client with quicker updates while still meeting contractual and firm guidelines."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Financial Analyst/Project Manager", "NAVAIR RIS Project (Booz Allen Hamilton)", "Lexington Park, MD", "Nov 2009 - Oct 2010", "Developed a financial tracking system for client, which allowed key stakeholders to view current and projected funding over the lifetime of the contract.",
        "Financial Analyst/Project Manager", "NAVAIR RIS Project (Booz Allen Hamilton)", "Lexington Park, MD", "Nov 2009 - Oct 2010", "Tracked current funding for multiple engineers and monitored the expenditures of funds on their contracts, which ensured that projects remained on budget."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

# Volunteer
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Organizer", "Data Jawn Conference", "Philadelphia, PA", "April 2019 - Present", "Assisted in promotion, speaker selection, and day-of-event logistics for the Data Jawn, a Philadelphia data conference highlighting the great work of our local data commnuity."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Data Analyst", "Montgomery County Public Defender", "Norristown, PA", "May 2016 - Jun 2017", "Assisted Montgomery County Public Defender to define an analytics strategy to support competitive salaries and fair defence for all Montgomery County residents.",
        "Data Analyst", "Montgomery County Public Defender", "Norristown, PA", "May 2016 - Jun 2017", "Created, built, and maintained advanced analysis."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

# Education
```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
        "Masters of Science - Applied Statistics", "Villanova University", "Villanova, PA", "2015 - 2017", "Completed my program while working full time"
        ) %>% detailed_entries(degree, dates, uni, loc, details)
```

```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative for Student Lobbying Day in Harrisburg, PA, 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Traditions Council Treasurer, 2007 - 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Dean’s List, 2006, 2008",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative to Colonial Athletic Association's Student Athlete Advisory Committee, 2006",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Varsity Soccer Player, 2004 - 2006"
        ) %>% detailed_entries(degree, dates, uni, loc, details)
```


\makecvfooter{`r format(Sys.time(), '%B %Y')`}{Jacob Rozran}{2}

