---
name: Jake Rozran
position: "Data Science Practice Lead & Adjunct Professor of Data Science"
address: "1400 Maryland Ave. Havertown, PA 19083"
phone: (410) 231-9371
www: jakelearnsdatascience.com
email: "jacob.rozran@gmail.com"
twitter: StatsManPHL
github: jrozra200
linkedin: jacob-rozran
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(VennDiagram)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Summary

In addition to being a dad, uncle, & data guy, I am a data & technology 
professional with real-world experience in data science, advocacy, building and 
growing teams, project management, sales, consulting, and teaching. I am curious 
about the changing landscape of technology's impact on our lives and especially 
passionate about fair and ethical algorithms. My passion for data and statistics 
has also inspired me to become an Adjunct Professor of Data Science & Statistics, 
which has improved my ability to explain complex subjects to all levels of 
understanding. 

# Top Skills & Technologies

\begin{center}

```{r, results = "asis"}
df <- data.frame(a = c("Data Ethics", "Data Visualization", 
                       "Data Analysis", "Project Management", 
                       "People Leadership"),
                 b = c("RStudio", "Jupyter Notebooks", "Tableau/Metabase/Redash", 
                       "GitHub", "MS Office Suite"),
                 c = c("SQL", "R", "Python", "Bash", "HTML"),
                 d = c("PostgreSQL", "Hive/Impala (Hadoop)", "Athena (AWS)", 
                       "SQL/mySQL/SQLite", "Neo4J"))

names(df) <- c("METHODS", "APPLICATIONS", "LANGUAGES", "DATABASES")

kable(df, row.names = FALSE, "latex", booktabs = T)
```
\end{center}

# Experience
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Data Science Practice Lead", "CivicActions", "Lafayette, CA", "Feb 2021 - Present", "Building a Data Science Practice Area with > $1MM revenue after 12 months; personally focused on data science, people management and coaching, sales, marketing, and project management.",
        "Data Science Practice Lead", "CivicActions", "Lafayette, CA", "Feb 2021 - Present", "For the Centers of Medicare and Medicaid (CMS), leveraging Natural Language Processing (NLP) in the creation and evaluation of System Security Plans (SSPs) to optimize the Authority to Operate (ATO) process; analyzing AWS usage to forecast annual usage and identify inefficiencies; using graph analysis and NLP to identify related documents to provide enhanced search capabilities.",
        "Data Science Practice Lead", "CivicActions", "Lafayette, CA", "Feb 2021 - Present", "One of five members of the company's Diversity, Equity, Inclusion, and Accessibility (DEIA) team; responsible for helping improve the company's DEIA practices, including analyzing demographic data, designing surveys to understand company feeling about DEIA, and identifying and improving company policy to be more inclusive.",
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Adjunct Professor of Data Science & Statistics", "Villanova University", "Villanova, PA", "Aug 2020 - Present", "Build the syllabus, lectures, assignments, projects, and tests for undergraduate Data Science, Intro to Statistics, and Intro to Statistics for Biology courses.",
        "Adjunct Professor of Data Science & Statistics", "Villanova University", "Villanova, PA", "Aug 2020 - Present", "Advise and mentor students by writing recommendations for various programs, helping guide studies for real-world success after graduation, and providing assistance through the stresses of university life. "
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Public Interest Technology - University Network (PIT-UN) Evaluation Committee", "New America", "Washington, DC", "June 2022 - Present", "Evaluate proposals seeking funding to educate students who can better apply technical understanding and practice to questions of individual rights, justice, social welfare, and the public good, particularly for those members of our society least well served historically and today by existing systems and policies"
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Solutions Consultant", "Socure", "New York, NY", "Jan 2020 - Feb 2021", "Technical expert on fraud prevention, Know Your Customer (KYC)/Customer Identification Program (CIP), Socure product modules, data science, statistics, and data visualization in support of the sales and onboarding processes.",
        "Solutions Consultant", "Socure", "New York, NY", "Jan 2020 - Feb 2021", "Created custom proof-of-concept (POC) analyses for prospective customers - showing the value of Socure versus their current solution(s).",
        "Solutions Consultant", "Socure", "New York, NY", "Jan 2020 - Feb 2021", "Served as the Growth Team's subject matter expert (SME) on data science, creating educational documents and presentations on challenging topics like Area Under the Curve (AUC), false positives, and other model evaluation criteria.",
        "Solutions Consultant", "Socure", "New York, NY", "Jan 2020 - Feb 2021", "Worked with the Marketing Team to create content for the Socure Blog on machine learning techniques.",
        "Solutions Consultant", "Socure", "New York, NY", "Jan 2020 - Feb 2021", "Member of the DEI team."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Jan 2020", "Lead and manage the data analytics and engineering team for Xfinity Mobile Credit Risk Management, including hiring and training of staff analysts and engineers, collaborating with and providing analysis for stakeholders, and tracking and prioritizing all team tasking.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Jan 2020", "Designed and built a fraud decision making tool that combines custom feature creation, statistical and business rules, and predictive models built in R, Python, and Bash, which, in large part, is responsible for a decrease in month-over-month fraud losses by 92% in 2018.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Jan 2020", "Provide coaching, leadership, and mentorship to all analysts on the Xfinity Mobile Risk Management team."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Designed and built predictive models, which improved compromised user account detection times and discovery accuracy – this work was presented internally along with several internal blog posts about the effort.", 
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Used statistical methods to discover and automate the detection of anomalies.", 
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Created forecasts of user base growth and project completion."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Apr 2013 - Sep 2014", "Served as a Project Manager and ScrumMaster for the Messaging Application Engineering (MAE) team, responsible for Residential Voicemail and Email Engineering teams.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Apr 2013 - Sep 2014", "Obtained my Project Management Professional (PMP) and Certified ScrumMaster (CSM) certifications.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Apr 2013 - Sep 2014", "Instituted and evangelized Scrum on both the email and voicemail teams, migrating from a hybrid of waterfall and Kanban, which led to higher team productivity, better communication across teams from development through deployment to production, and improved interaction with our product owners."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Implementation Manager", "NCS Main Study Information Management Systems Project (Booz Allen Hamilton)", "Rockville, MD", "Nov 2010 - Apr 2013", "Served as the Implementation Manager and Site Administrator for the National Children’s Study (NCS) Portal, a Microsoft SharePoint 2010 web application, the NCS Application Homepage, and NCS Password Self Service."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Financial Analyst/Project Manager", "NAVAIR RIS Project (Booz Allen Hamilton)", "Lexington Park, MD", "Nov 2009 - Oct 2010", "Developed a financial tracking system for client, which allowed key stakeholders to view current and projected funding over the lifetime of the contract."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

# Volunteer
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Resident Data Science Expert", "Govern for America", "Katonah, NY", "April 2022 - Present", "Provide training and mentorship in data science, data visualization, and data ethics for GFA fellows."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Organizer", "Data Jawn Conference", "Philadelphia, PA", "April 2019 - Present", "Assisted in promotion, speaker selection, and day-of-event logistics for the Data Jawn, a Philadelphia data conference highlighting the great work of our local data commnuity."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Data Analyst", "Montgomery County Public Defender", "Norristown, PA", "May 2016 - Jun 2017", "Assisted Montgomery County Public Defender to define an analytics strategy to support competitive salaries and fair defence for all Montgomery County residents; created, built, and maintained advanced analysis."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

# Education
```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, 
        "Masters of Science - Applied Statistics", "Villanova University", "Villanova, PA", "2015 - 2017"
        ) %>% detailed_entries(degree, dates, uni, loc)
```

```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative for Student Lobbying Day in Harrisburg, PA, 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Traditions Council Treasurer, 2007 - 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Dean’s List, 2006, 2008",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative to Colonial Athletic Association's Student Athlete Advisory Committee, 2006",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Varsity Soccer Player, 2004 - 2006"
        ) %>% detailed_entries(degree, dates, uni, loc, details)
```

