---
name: Jacob Rozran - US Citizen
position: "Data Science Practice Lead & Adjunct Professor of Data Science"
address: "1400 Maryland Ave. Havertown, PA 19083"
phone: (410) 231-9371
www: jakelearnsdatascience.com
email: "jacob.rozran@gmail.com"
twitter: StatsManPHL
github: jrozra200
linkedin: jacob-rozran
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: vitae::awesomecv
---

```{r setup, include = FALSE}
library(vitae)
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Application Information

**Title:** Senior Technologist - IT Specialist (Policy and Planning)  
**Agency:** Consumer Financial Protection Bureau (CFPB)  
**Announcement Number:** 22-CFPB-297-X  
**Grade Level:** CN 71  
**Location:** Remote (I reside in Havertown, PA)  

# Personal Summary

In addition to being a dad, uncle, & data guy, I am a data & technology 
professional with real-world experience in data science, advocacy, building and 
growing teams, project management, sales, consulting, and teaching. I am curious 
about the changing landscape of technology's impact on our lives and especially 
passionate about fair and ethical algorithms. My passion for data and statistics 
has also inspired me to become an Adjunct Professor of Data Science & Statistics, 
which has improved my ability to explain complex subjects to all levels of 
understanding. 

# Top Skills & Technologies

\begin{center}

```{r, results = "asis"}
df <- data.frame(a = c("Data Ethics", "Data Visualization", 
                       "Data Analysis", "Project Management", 
                       "People Leadership"),
                 b = c("RStudio", "Jupyter Notebooks", "Tableau/Metabase/Redash", 
                       "GitHub", "MS Office Suite"),
                 c = c("SQL", "R", "Python", "Bash", "HTML"),
                 d = c("PostgreSQL", "Hive/Impala (Hadoop)", "Athena (AWS)", 
                       "SQL/mySQL/SQLite", "Neo4J"))

names(df) <- c("METHODS", "APPLICATIONS", "LANGUAGES", "DATABASES")

kable(df, row.names = FALSE, "latex", booktabs = T)
```
\end{center}

# Experience

## CivicActions

**Title:** Data Science Practice Lead (Remote)  
**Company Location:** 3527 Mt. Diablo Blvd., Unit 269, Lafayette, CA  
**Supervisor (please do not contact):** Bill Ogilvie, Vice President of Sales, 
(202) 415-0947  
**Dates of Employment:** February 22, 2021 - Present  
**Hours per Week:** Full-time (40 hours per week)  
**Salary:** $165,000 (Other benefits not included in salary number)  
**Duties and Accomplishments:**

- Building a Data Science Practice Area with > $1MM revenue after 12 months; 
personally focused on data science, people management and coaching, sales, 
marketing, and project management.
- For various clients at the Centers of Medicare and Medicaid (CMS): 
    - Leveraging Natural Language Processing (NLP) in the creation, evaluation, 
    and summarization of System Security Plans (SSPs) to optimize the Authority 
    to Operate (ATO) process. Technologies used: Python, R, Rmd, GitHub, GitHub 
    Pages.
    - Analyzing AWS usage data to investigate misuse of resources, forecast 
    annual usage, identify inefficiencies, and alert on anomalies. Technologies 
    used: R, Shiny Dashboards, AWS Athena, GitHub.
    - Using graph analysis and NLP to identify related documents for 
    enhanced search capabilities. Technologies used: R, Rmd, GitHub.
- One of five members of the company's Diversity, Equity, Inclusion, and 
Accessibility (DEIA) team.
    - Responsible for helping improve the company's DEIA practices, including 
    analyzing demographic data, designing surveys to understand company feeling 
    about DEIA, and identifying and improving company policy to be more 
    inclusive. Technologies used: R, Rmd, CultureAmp, GitHub.

---

## Villanova University

**Title:** Adjunct Professor of Data Science and Statistics  
**University Location:** 800 Lancaster Avenue, Villanova, PA  
**Supervisor:** Dr. Jesse Frey, Department of Mathematics and Statistics 
Chairperson, (610) 519-4850  
**Dates of Employment:** August 10, 2020 - Present  
**Hours per Week:** Part-time (~15 hours per week during the semester)  
**Salary:** $8,700 (\$1,450 per credit hour)  
**Duties and Accomplishments:**  

- Build the syllabus, lectures, assignments, projects, and tests for 
undergraduate Data Science, Intro to Statistics, and Intro to Statistics for 
Biology courses.
- Advise and mentor students by writing recommendations for various programs, 
helping guide studies for real-world success after graduation, and providing 
assistance through the stresses of university life. 

---

## New America

**Title:** Public Interest Technology - University Network (PIT-UN) Evaluation 
Committee Member (Remote)  
**Company Location:** 740 15th Street NW, Suite 900, Washington, DC  
**Supervisor:** NA  
**Dates of Employment:** May 27, 2022 - July 18, 2022  
**Hours per Week:** Part-time (~5 hours per week during the evaluation period)  
**Salary:** $650  
**Duties and Accomplishments:**  

- Evaluate proposals seeking funding to educate students who can better apply 
technical understanding and practice to questions of individual rights, justice, 
social welfare, and the public good, particularly for those members of our 
society least well served historically and today by existing systems and 
policies

---

## Socure

**Title:** Solutions Consultant (Remote)  
**Company Location:** 885 Tahoe Blvd Suite 11, Incline Village, NV  
**Supervisor:** Garient Evans, Vice President of Growth, (858) 945-3515 (No 
longer at Socure)  
**Dates of Employment:** January 13, 2020 - February 12, 2021  
**Hours per Week:** Full-time (40 hours per week)  
**Salary:** $150,000 + Sales Incentive (paid quarterly up to \$75,000)  
**Duties and Accomplishments:**  

- Technical expert on fraud prevention, Know Your Customer (KYC)/Customer 
Identification Program (CIP), Socure product modules, data science, statistics, 
and data visualization in support of the sales and onboarding processes.
- Created custom proof-of-concept (POC) analyses for prospective customers - 
showing the value of Socure versus their current solution(s).
- Served as the Growth Team's subject matter expert (SME) on data science, 
creating educational documents and presentations on challenging topics like Area 
Under the Curve (AUC), false positives, and other model evaluation criteria.
- Worked with the Marketing Team to create content for the Socure Blog on 
machine learning techniques.
- Member of the DEI team.

---

## Comcast

**Title:** Manager of Data Analytics - Xfinity Mobile Risk Management  
**Company Location:** 1701 John F. Kennedy Blvd., Philadelphia, PA  
**Supervisor:** Mike McCabe, Executive Director of Credit Risk Management, 
(913) 485-3592 (No longer at Comcast)  
**Dates of Employment:** March 20, 2017 - January 10, 2020  
**Hours per Week:** Full-time (40 hours per week)  
**Salary:** ~$120,000 (Other benefits not included in salary number)  
**Duties and Accomplishments:**  

- Designed, built, deployed, maintained, and monitored a fraud decision making 
tool that combines custom feature creation, statistical and business rules, and 
predictive models, which, in large part, is responsible for a decrease in month-over-month fraud losses by 92% in 2018. Technologies Used: R, Python, 
Random Forest, Cloudera Hadoop (Impala), OracleDB, Tableau, Rmd, and GitHub.
- Led and managed the data analytics and engineering team for Xfinity Mobile 
Credit Risk Management, including hiring and training of staff analysts and 
engineers, collaborating with and providing analysis for stakeholders, and 
tracking and prioritizing all team tasking.
- Provide coaching, leadership, and mentorship to all analysts on the Xfinity 
Mobile Risk Management team.

---

## Comcast

**Title:** Senior Data Analyst - Internet Services Engineering  
**Company Location:** 1701 John F. Kennedy Blvd., Philadelphia, PA  
**Supervisor:** Tom Payne, Senior Manager of Insights and Analytics, 
(202) 210-2120  
**Dates of Employment:** September 15, 2014 - March 17, 2017  
**Hours per Week:** Full-time (40 hours per week)  
**Salary:** ~$95,000 (Other benefits not included in salary number)  
**Duties and Accomplishments:**  

- Designed and built predictive models, which improved compromised user account 
detection times and discovery accuracy – this work was presented internally 
along with several internal blog posts about the effort. Technologies Used: R, 
Splunk, Logistic Regression, and Microsoft Excel.
- Used statistical methods to discover and automate the detection of anomalies.
- Created forecasts of user base growth and project completion.

---

## Comcast

**Title:** Project Manager - Messaging Application Engineering  
**Company Location:** 1701 John F. Kennedy Blvd., Philadelphia, PA  
**Supervisor:** Jordan Rosenwald, Director of Software Development & 
Engineering, (856) 448-4767  
**Dates of Employment:** April 22, 2013 - September 12, 2014  
**Hours per Week:** Full-time (40 hours per week)  
**Salary:** ~$72,000 (Other benefits not included in salary number)  
**Duties and Accomplishments:**  

- Served as a Project Manager and ScrumMaster for the Messaging Application 
Engineering (MAE) team, responsible for Residential Voicemail and Email 
Engineering teams.
- Obtained my Project Management Professional (PMP) and Certified ScrumMaster 
(CSM) certifications.
- Instituted and evangelized Scrum on both the email and voicemail teams, 
migrating from a hybrid of waterfall and Kanban, which led to higher team 
productivity, better communication across teams from development through 
deployment to production, and improved interaction with our product owners.

---

## Booz Allen Hamilton (BAH)

**Title:** Senior Consultant & Implementation Manager - National Institutes of 
Health (NIH) Eunice Kennedy Shriver National Institute of Child Health and Human 
Services (NICHD) National Children's Study (NCS) Main Study Information 
Management Systems Project  
**Company Location:** 8283 Greensboro Drive, McLean, VA  
**Project Location:** One Preserve Parkway, Rockville, MD  
**Supervisor:** Christian Sauter, Lead Associate, (856) 625-5332 (no longer with 
BAH)  
**Dates of Employment:** November 8, 2010 - April 12, 2013  
**Hours per Week:** Full-time (40 hours per week)  
**Salary:** ~$50,000 (Other benefits not included in salary number)  
**Duties and Accomplishments:**  

- Served as the Implementation Manager and Site Administrator for the National 
Children’s Study (NCS) Portal, a Microsoft SharePoint 2010 web application, the 
NCS Application Homepage, and NCS Password Self Service.

---

## Booz Allen Hamilton (BAH)

**Title:** Consultant & Financial Analyst/Project Manager - NAVAIR Radio 
Information Systems (RIS) Project  
**Company Location:** 8283 Greensboro Drive, McLean, VA  
**Project Location:** Naval Outlying Field Webster, St. Inigoes, MD  
**Supervisor:** NA  
**Dates of Employment:** November 2, 2009 - November 5, 2010  
**Hours per Week:** Full-time (40 hours per week)  
**Salary:** $42,000 (Other benefits not included in salary number)  
**Duties and Accomplishments:**  

- Developed a financial tracking system for client, which allowed key 
stakeholders to view current and projected funding over the lifetime of the 
contract.

# Volunteer

## Govern for America

**Title:** Resident Data Science Expert (Remote)  
**Company Location:** 107 North Salem Road, Katonah, NY  
**Supervisor:** Talita Elizeu, Alumni & Community Engagement Director, 
(617) 435-9200  
**Dates of Involvement:** April 8, 2022 - Present  
**Hours per Week:** Part-time  
**Duties and Accomplishments:**  

- Provide training and mentorship in data science, data visualization, and data 
ethics for GFA fellows.

---

## Data Jawn Conference

**Title:** Organizer (Remote)  
**Supervisor:** Dan Larson, Founder and Lead, (484) 560-5753  
**Dates of Involvement:** April 20, 2019 - Present  
**Hours per Week:** Part-time  
**Duties and Accomplishments:**  

- Assist in promotion, speaker selection, and day-of-event logistics for the 
Data Jawn, a Philadelphia data conference highlighting the great work of our 
local data commnuity.

---

## Montgomery County Public Defender

**Title:** Data Analyst (Remote)  
**Company Location:** P.O. Box 311, Norristown, PA  
**Supervisor:** Dean Beer, Chief Public Defender, (610) 246-7613 (no longer at 
Public Defender's office)  
**Dates of Involvement:** May 9, 2016 - June 5, 2017  
**Hours per Week:** Part-time  
**Duties and Accomplishments:**  

- Assisted Montgomery County Public Defender to define an analytics strategy to support competitive salaries and fair defence for all Montgomery County residents; created, built, and maintained advanced analysis.

# Education

## Villanova Unversity 

**University Location:** 800 Lancaster Avenue, Villanova, PA  
**Degree Awarded:** Masters of Science in Applied Statistics  
**Date Received:** May 12, 2017  
**GPA:** 3.53  

---

## Drexel Unversity 

**University Location:** 3141 Chestnut Street, Philadelphia, PA  
**Degree Awarded:** Bachelors of Science in Business & Engineering  
**Date Received:** June 5, 2009  
**GPA:** 3.22  

