---
name: Jake
surname: Rozran
position: "Data Professional & Adjunct Professor"
address: "1400 Maryland Ave. Havertown, PA 19083"
phone: (410) 231-9371
www: jakelearnsdatascience.com
email: "jacob.rozran@gmail.com"
twitter: StatsManPHL
github: jrozra200
linkedin: jacob-rozran
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
options(tinytex.verbose = TRUE)
```

# About Me

In addition to being a leader, dad, uncle, & data guy, I am a data & technology 
professional with real-world experience in data science, data analytics, data 
engineering, fraud detection, risk modeling, building and maintaining data teams, 
project management, sales, consulting, and teaching. 

My passion for data and statistics has inspired me to become an Adjunct 
Professor of Statistics, which has improved my ability to explain complex 
subjects to all levels of understanding. I love to learn in general and am a 
data fanatic.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
  "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
  "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

